WWII Events Reduce Population in One Shanghai District While Increasing It in Others

### 2024-12-02 paper/paper.qmd
added title and changed formatting

---
title: "My title"
subtitle: "Impact Analysis of Japanese Occupation on Population Shifts Across Shanghai’s Districts During WWII"
author: 
  - Sandy Yu
thanks: "Code and data are available at: https://github.com/Jingying-yu/Shanghai_population_change"
date: today
date-format: long
abstract: "This paper evaluates the impact of three historic events on the population dynamics of Shanghai during WWII: the Japanese occupation of the Chinese-administered area, France’s surrender in WWII, and the Japanese occupation of the International Settlement. Data from the Virtual Shanghai research platform and historic publications are analyzed using a difference-in-difference model to estimate the effects of these events. The results indicate that the Japanese occupation of the Chinese-administered area led to an overall increase in Shanghai’s population across all districts. In contrast, France’s surrender during WWII had a negative impact on population numbers in all districts except the French Concession. Similarly, the Japanese occupation of the International Settlement caused population declines in all districts except the International Settlement itself. These findings underscore the complex demographic shifts resulting from geopolitical events and reveal how wartime occupation reshaped urban populations in uneven ways, reflecting resilience and displacement patterns."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

Where:

@@

Interaction Terms:

@@

# Appendix B: Idealized Survey Methodology

>>>>

---
title: "WWII Events Reduce Population in One Shanghai District While Increasing It in Others"
subtitle: "Impact Analysis of Japanese Occupation on Population Shifts Across Shanghai’s Districts During WWII"
author: 
  - Sandy Yu
thanks: "Code and data are available at: https://github.com/Jingying-yu/Shanghai_population_change"
date: today
date-format: long
abstract: "This paper evaluates the impact of three historic events on the population dynamics of Shanghai during WWII: the Japanese occupation of the Chinese-administered area, France’s surrender in WWII, and the Japanese occupation of the International Settlement. Data from the Virtual Shanghai research platform and historic publications are analyzed using a difference-in-difference model to estimate the effects of these events. The results indicate that the Japanese occupation of the Chinese-administered area led to an overall increase in Shanghai’s population across all districts. In contrast, France’s surrender during WWII had a negative impact on population numbers in all districts except the French Concession. Similarly, the Japanese occupation of the International Settlement caused population declines in all districts except the International Settlement itself. These findings underscore the complex demographic shifts resulting from geopolitical events and reveal how wartime occupation reshaped urban populations in uneven ways, reflecting resilience and displacement patterns."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

**Where**:

@@

**Interaction Terms**:

@@

# Idealized Survey Methodology
